\textbf{Response Letter}

### 2018-12-21 doc/aij18/major-revision/letter.tex
Comments related to section 3 answered

\textcolor{blue}{Following the reviewer's advice, we have substantially changed section 3. We refer the reviewer to our main modification \#2. We removed the complexity table of page 8 and we now focus the discussion around the two main cases that determine the difficulty of the learning task, giving an indication of the task complexity according to the characteristics that define these two cases. We also changed the reference and added instead the original work that proves that boolean SAT problems are NP-complete.}

@@

@@

\textcolor{blue}{The reviewer is totally right in that planning is needed when the length of the solution plan is unknown. Precisely, this is the point that motivates our approach but that we did not successfully convey in the previous version of the paper. When the observed plan trace comprises a partially observed action sequence and a partially observed state trajectory, we ignore the length of the solution plan and so we need to resort to planning. The new section 3 explains this in detail (main modification \#2). When the length of the plan is known, SAT-solvers can be used; when it is not known, planning is required. The fact that we used a SAT-based planner to solve the learning task is principally motivated by the ability of Madagascar to detect dead-end nodes.}

@@

\textcolor{blue}{We think the paragraph was rather confusing and that we did not clearly come through our intention to set an analogy between the data sources used in explainable AI and the data required by the learning approaches. For this reason, we have removed the paragraph and instead we include a list of planning-related tasks that require a planning model for being solved. We think this rather complete but non-exhaustive list is a pretty good indication of the need for learning planning models.}

@@

 We changed the title as recommended by the reviewer.

>>>>

\textcolor{blue}{Following the reviewer's advice, we have substantially changed section 3. We refer the reviewer to our main modification \#2. We removed the complexity table of page 8, focusing now the discussion around the two main cases that determine the difficulty of the learning task and giving an indication of the task complexity according to the characteristics that define these two cases. We also changed the reference and added instead the original work that proves that boolean SAT problems are NP-complete.}

\textcolor{blue}{The take-home lesson of section 3 is that when the observed plan trace does not provide information of the solution plan length (case 2), planning is needed to find the solution and so the learning task is PSPACE-complete.}

@@

\textcolor{red}{FALTA .... }

@@

\textcolor{blue}{The reviewer is totally right in that planning is needed when the length of the solution plan is unknown. Precisely, this is the point that motivates our approach but that we did not successfully convey in the previous version of the paper. When the observed plan trace comprises a partially observed action sequence and a partially observed state trajectory, we ignore the length of the solution plan and so we need to resort to planning. The new section 3 explains this in detail (main modification \#2). When the length of the plan is known, SAT-solvers can be used; when it is not known, planning is required. In our case, we use a planner to solve all learning tasks independently of their nature.}

\textcolor{blue}{On the other hand, we happen to use a SAT-based planner (Madagascar) for solving the learning tasks, which may lead to wrongly interpret that the length of the solution plan is always known. The reasons for using Madagascar have been highlighted in red at the beginning of section 6. In a nutshell, we use Madagascar because it returned the best results compared to other planners and because of its ability to handle problems with dead-ends. Additionally, Madagascar is obviously very suitable to solve learning tasks when the length of the plan is known.}

@@

\textcolor{blue}{We think the paragraph was rather confusing and that we did not clearly come through our intention to set an analogy between the data sources used in explainable AI and the data required by the learning approaches. For this reason, we have removed the paragraph and included instead a list of planning-related tasks that require a planning model for being solved. We think this rather complete but non-exhaustive list is a pretty good indication of the need for learning planning models.}

@@

\textcolor{blue}{We changed the title as recommended by the reviewer.}
